Case study validations of automatic bullet matching

### 2018-10-09 index.Rmd

What is quite surprising, that what we anticipated to be the easiest case of Hamby 44 turned out to be the hardest to solve.

# Appendix

\autoref{fig:tankrash} shows an overview of all lands of bullets in the Hamby-44 with major deficiencies, such as 'tank rash' or extreme pitting (holes caused by direct contact with burning gun powder).
```{r tankrash, fig.cap="Overview of bullet lands with prominent deficiency such as tank rash or extreme pitting in the Hamby-44 study.", fig.width=4, fig.height = 2, out.width='47.5%', fig.subcap=c("Br1-B1-L6", "Br2-B2-L5", "Br3-B1-L5", "Br8-B1-L6", "Br8-B2-L2", "Br8-B2-L6", "Unk-E-L6", "Unk-I-L6"), fig.align="middle", fig.ncol=2}
knitr::include_graphics(
  c(
    "./images/B1-B1-L6.png", "./images/B2-B2-L5.png",
    "./images/B3-B1-L5.png", "./images/B8-B1-L6.png",
    "./images/B8-B2-L2.png", "./images/B8-B2-L6.png",
    "./images/NA-BE-L6.png", "./images/NA-BI-L6.png"
  )
)
```

Three lands across the two known bullets of barrel 8 are affected. This is the likely cause for the low scores for barrel 8 in \autoref{fig:h44}.

### Limitations
All of the studies involve the same firearm. We see some variations in scores across different models of Rugers. Likely, we are going to see even bigger variations with different brands of firearms, where there might be different number of lands of different lengths. We also know \cite{???} that different firearms mark differently well. Rugers are among the firearms that mark very well, so we would correspondingly expect to see lowered similarity scores for other firearms. The matching algorithm works on matching lands. Barrels with polygonal rifling, such as Glocks, do not introduce well defined lands on bullets, which makes an application of the matching algorithm impossible.

XXX Should we include some Sig Sauer matches?

>>>>

What is quite surprising, that what we anticipated to be the easiest case of Hamby 44 turned out to be the hardest to solve. 
This is likely due to several lands in the Hamby-44 set having major deficiencies,  such as 'tank rash' (a collision of the bullet after exiting the barrel with a surface causing markings on top of the striations from the barrel) or extreme pitting (holes caused by direct contact with burning gun powder).
\autoref{fig:tankrash} gives an overview of all lands of bullets in the Hamby-44 set affected. 
```{r tankrash, fig.cap="Overview of bullet lands with prominent deficiency such as tank rash or extreme pitting in the Hamby-44 study.", fig.width=4, fig.height = 2, out.width='47.5%', fig.subcap=c("Br1-B1-L6", "Br2-B2-L5", "Br3-B1-L5", "Br8-B1-L6", "Br8-B2-L2", "Br8-B2-L6", "Unk-E-L6", "Unk-I-L6"), fig.align="middle", fig.ncol=2}
knitr::include_graphics(
  c(
    "./images/B1-B1-L6.png", "./images/B2-B2-L5.png",
    "./images/B3-B1-L5.png", "./images/B8-B1-L6.png",
    "./images/B8-B2-L2.png", "./images/B8-B2-L6.png",
    "./images/NA-BE-L6.png", "./images/NA-BI-L6.png"
  )
)
```

Three lands from bullets known to be fired from barrel 8 are affected. This is the likely cause for the low scores for barrel 8 in \autoref{fig:h44}. We also see that questioned bullet 'E' is affected, explaining some of the low similarity scores for this bullet.

### Limitations
All of the studies involve the same firearm. We see some variations in scores across different models of Rugers. Likely, we are going to see even bigger variations with different brands of firearms, where there might be different number of lands of different lengths. We also know  that different firearms mark differently well \cite{???}. Rugers are among the firearms that mark very well, so we would correspondingly expect to see lowered similarity scores for other firearms. The matching algorithm works on matching lands. Barrels with polygonal rifling, such as Glocks, do not introduce well defined lands on bullets, which makes an application of the matching algorithm impossible.

As seen in the earlier discussion, similarity scores are affected by deficiencies on lands. It has been shown \citet{lpr} that parts of lands can be used for successful identifications. The  algorithm proposed by \citet{aoas} is not capable of  automatically detecting parts of lands with well expressed striae. XXX citation for neural network algorithm
